---
title: "Dystonia study - WGCNA - `r toupper(region)`"
author: "Darren Cameron"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

## hdWGCNA {.tabset}

***

It's not possible to run standard WGCNA analyses on single cell data due to data 
sparsity (i.e. an excess of zero values). To reduce sparsity, [hdWGCNA](https://www.cell.com/cell-reports-methods/fulltext/S2667-2375(23)00127-3)
uses a KNN approach to aggregate single cells with similar GeX profiles into metacells. 
Gene co-expression networks, and gene modules, can then be identified using WGCNA on
said metacells.

***

**Method for hdWGCNA**

1. Run hdWGCNA pipeline to find co-expression modules (default settings)
2. Run GO Analysis on all modules on the following databases:
  + GO_Biological_Process_2023
  + GO_Cellular_Component_2023
  + GO_Molecular_Function_2023
3. Take top 50 hub genes from each module and check for overlap with 25 dystonia genes
4. If there is at least a single gene overlap extract top 20 GO terms (Padj < 0.05) and plot
5. Modules are excluded if there is no gene overlap with 25 dystonia genes or no GO Terms at Padj < 0.05
6. Only ExN or InN cell types tested
7. Cells excluded if no valid Power Threshold could be generated (usually too few cells)

***

### Param settings {.tabset}

+ Running hdWGCNA on `r cell_type`
+ Gene selected using: `r gene_select`
+ k set to: `r set_k`
+ Aggregate cells: `r aggregate_cells`
+ Combine Seurat objects: `r aggregate_misc`

#### Stats table 

```{r cell_counts, results='asis', echo=FALSE}
knitr::kable(wgcna_stats_tbl)
```

#### Overlap genes

```{r overlap_genes, results='asis', echo=FALSE}
knitr::kable(bind_rows(overlap_genes))
```

***

#### hdWGCNA Plots {.tabset}

***

##### Dendogram

```{r dendo_plot, fig.dim = c(5,5), results='asis', echo=FALSE}
PlotDendrogram(seurat_obj, main = paste0(cell_type, ' hdWGCNA Dendrogram'))
```

***

##### kME

```{r kme_plot, fig.dim = c(10,10), echo=FALSE, results='hide', fig.keep='all'}
PlotKMEs(seurat_obj, ncol = 5)
```

***

#### GO plots {.tabset}

+ Plots show (at most) the top 20 GO terms with Padj < 0.05. 
+ Note modules with no terms with Padj < 0.05 not plotted

***

```{r go_mod_tbl, results='asis', echo=FALSE}
knitr::kable(go_module_tbl)
```

***

```{r go_plts, results='asis', echo=FALSE, fig.dim = c(20,20)}
for(module in module_overlaps) {
  cat("  \n##### ", module, "\n", sep = "")
  plot(plot_list[[module]])
  cat(' \n')
}

```

***



