---
title: "Dystonia study - Stiletti data analysis - 3rd Pass - `r toupper(region)`"
author: "Darren Cameron"
date: "`r Sys.Date()`"
output: html_document
---

*** 

### **Thresholds** {.tabset}

+ Biol Psych thresholds set for fetal samples
  + Cells exp < 1000 genes > 5000 genes (used 3 X MAD [high only] for adult)
  + gt 5% mito
  + gt 10% ribo (used 5% for adult)
  + Genes from mito genome excluded
  + Genes expressed in fewer than 3 cells excluded
  + Doublets - will skipped for now as done by Stiletti and likely resource intensive
  + Note: Big difference in UMI / Genes captured across adult and vs. fetal may be worth down-sampling as control / check

***

#### Diagnostics {.tabset}

##### Pre-filter

***

```{r plots_pre_filt, results='asis', fig.dim = c(20,20), echo=FALSE}
qc_plot_noFilt
```

***

```{r counts_pre_filt, results='asis', echo=FALSE}
knitr::kable(counts, caption = paste0("Counts: ", toupper(region)))
```

***

```{r umi_dist_pre_filt, results='asis', echo=FALSE}
knitr::kable(dist_counts_noFilt, caption = paste0("UMI and gene count distribution summary: ", toupper(region)))
```

***

##### Outliers

```{r outlier_plot, results='asis', fig.dim = c(20,20), echo=FALSE}
cell_outlier_plot
```

***

```{r outlier_cnts_tbl, results='asis', echo=FALSE}
knitr::kable(cell_outlier_cnts_tbl, caption = paste0("Cell outlier counts: ", toupper(region)))
```

***

##### Post-filter

***

```{r plots_post_filt, results='asis', fig.dim = c(20,20), echo=FALSE}
qc_plot_post_Filt
```

***

```{r counts_post_filt, results='asis', echo=FALSE}
knitr::kable(counts_post_Filt, caption = paste0("Counts: ", toupper(region)))
```

***

```{r umi_dist_post_filt, results='asis', echo=FALSE}
knitr::kable(dist_counts_post_Filt, caption = paste0("UMI and gene count distribution summary: ", toupper(region)))
```

***

#### Cluster QC Plots {.tabset}

+ Note that NAs are generated as we're using a Sketch object here (i.e. only 5K cells)
+ Batch effects clear best when using sample id
+ Get cell counts per cluster

***

```{r cluster_qc_plots, results='asis', fig.dim = c(20,20), echo=FALSE}
cluster_qc_plot
```

***

#### Resolution {.tabset}

+ Checking res params for range from 0.1 - 0.8 (latter is the Seurat default)
+ I'm leaning towards setting this to 0.1 as these map quite well to the original Stiletti annotations

***

```{r resolution, fig.dim = c(20, 20), echo = FALSE, results="asis"}
for(i in resolution_set) {
  cat("  \n##### **", i , "**\n", sep = "")
  plot_subset <- res_plotlist[grep(i, names(res_plotlist), ignore.case = TRUE)]
  plot(cowplot::plot_grid(plotlist = plot_subset, ncol = 2))
  cat("  \n")
}
```

***

#### Integration Plots {.tabset}

+ Integration done on sample ID, i.e. lane 
+ Running on resolution 0.1 - the lowest setting

***

```{r Integration plots, fig.dim = c(20, 20), echo = FALSE, results="asis"}
for(i in resolution_set) {
  cat("  \n##### **", i , "**\n", sep = "")
  plot_subset <- integration_plotlist[grep(i, names(integration_plotlist), ignore.case = TRUE)]
  plot(cowplot::plot_grid(plotlist = plot_subset, ncol = 2))
  cat("  \n")
}
```

***

#### Paired vln (General) 

***

+ harmony_clusters_0.1
+ Left: General brain gene set
+ Right: More region specific gene set

```{r paired_vln, results='asis', fig.dim = c(10,10), echo=FALSE}
vln_plots
```

***
