---
title: "Dystonia study - Annotation - `r toupper(region)`"
author: "Darren Cameron"
date: "`r Sys.Date()`"
output: html_document
---

### Annotations {.tabset}

***

#### Sketch {.tabset}

##### Paired vln (General) {.tabset}

***

+ Left: General brain gene set
+ Right: More region specific gene set

```{r paired_vln_sketch, results='asis', fig.dim = c(10,10), echo=FALSE}
vln_plots_sketch
```

***

##### UMAP and vln (dystonia genes) 

***

+ Broad agreement between Stiletti annotations (see qc html) and ours 

```{r umap_vln_plots_sketch, results='asis', fig.dim = c(10,10), echo=FALSE}
umap_vln_plots_sketch
```

***

##### Dystonia genes

***

```{r cluster_umap_sketch, results='asis', fig.dim = c(10,10), echo=FALSE}
dystonia_plot_sketch
```

***


#### RNA {.tabset}

##### Paired vln (General) {.tabset}

***

+ Left: General brain gene set
+ Right: More region specific gene set

```{r paired_vln_rna, results='asis', fig.dim = c(10,10), echo=FALSE}
vln_plots_rna
```

***

##### UMAP and vln (dystonia genes) 

***

+ Broad agreement between Stiletti annotations (see qc html) and ours 

```{r umap_vln_plots_rna, results='asis', fig.dim = c(10,10), echo=FALSE}
umap_vln_plots_rna
```

***

##### Dystonia genes

***

```{r cluster_umap_rna, results='asis', fig.dim = c(10,10), echo=FALSE}
dystonia_plot_rna
```

***

#### Refs

***

+ Striatal genes: [Anderson et al (2023)](10.1038/s41598-023-36255-5)
+ Cer genes: [Zhong et al (2023)](https://doi.org/10.1038/s41467-023-43568-6)

***