---
title: "Dystonia study - WGCNA - `r toupper(region)`"
author: "Darren Cameron"
date: "`r Sys.Date()`"
output: html_document
---

### hdWGCNA {.tabset}

***

It's not possible to run standard WGCNA analyses on single cell data due to data 
sparsity (i.e. an excess of zero values). To reduce sparsity, [hdWGCNA](https://www.cell.com/cell-reports-methods/fulltext/S2667-2375(23)00127-3)
uses a KNN approach to aggregate single cells with similar GeX profiles into metacells. 
Gene coexpression networks, and gene modules, can then be identified using WGCNA on
said metacells.

The rationale for using this is to 

#### Regional info {.tabset}

+ Running hdWGCNA on `r toupper(region)`
+ Gene selected using: `r gene_select`
+ k set to: `r set_k`
+ Aggregate cells: `r aggregate_cells`
+ Combine Seurat objects: `r aggregate_misc`

##### Cell props {.tabset}

###### Counts

```{r cell_counts, results='asis', echo=FALSE}
knitr::kable(table(seurat_obj$cellIDs))
```

###### Proportions

***

Compare cluster and meta-cluster proportions

```{r cell_props, results='asis', echo=FALSE}
knitr::kable(cell_props$orig, "html", caption ="Original cluster proportions") %>%
kableExtra::kable_styling(bootstrap_options = c("hover"),
                            full_width = FALSE, position = "float_left")

knitr::kable(cell_props$meta, "html", caption ="Metacell cluster proportions") %>%
kableExtra::kable_styling(bootstrap_options = c("hover"),
                          full_width = FALSE, position = "float_right")
```

***

###### Cells removed

***

Clusters removed (per donor) with cells < 100

```{r clusters_rm, results='asis', echo=FALSE}
cat(clusters_rm, sep="\n")
```

***

##### Plots {.tabset}

***

Dendogram

```{r dendo_plot, fig.dim = c(10,10), results='asis', echo=FALSE}
#PlotDendrogram(seurat_obj, main = paste0(cell_type, ' hdWGCNA Dendrogram'))
```

***

kME

```{r kme_plot, fig.dim = c(10,10), echo=FALSE, results='hide', fig.keep='all'}
#PlotKMEs(seurat_obj, ncol = 5)
```

***

##### WGCNA output {.tabset}

###### Overlap genes

```{r overlap_genes, results='asis', echo=FALSE}
knitr::kable(bind_rows(overlap_genes))
```

***

###### Stats

```{r overlap_stats, results='asis', echo=FALSE}
knitr::kable(wgcna_stats_tbl)
```

***
