---
title: "Dystonia study - Annotation - `r toupper(region)`"
author: "Darren Cameron"
date: "`r Sys.Date()`"
output: html_document
---

### Annotations {.tabset}

***

#### Sketch {.tabset}

##### Paired vln (General) {.tabset}

***

+ Left: General brain gene set
+ Right: More region specific gene set

```{r paired_vln_sketch, results='asis', fig.dim = c(10,10), echo=FALSE, warning=FALSE}
vln_plots_sketch
```

***

##### UMAP and vln (dystonia genes) 

***

+ Broad agreement between Stiletti annotations (see qc html) and ours 

```{r umap_vln_plots_sketch, results='asis', fig.dim = c(10,10), echo=FALSE, warning=FALSE}
umap_vln_plots_sketch
```

***

##### Dystonia genes

***

```{r cluster_umap_sketch, results='asis', fig.dim = c(10,10), echo=FALSE, warning=FALSE}
dystonia_plot_sketch
```

***


#### RNA {.tabset}

##### Paired vln (General) {.tabset}

***

+ Left: General brain gene set
+ Right: More region specific gene set

```{r paired_vln_rna, results='asis', fig.dim = c(10,10), echo=FALSE, warning=FALSE}
vln_plots_rna
```

***

##### UMAP and vln (dystonia genes) 

***

+ Broad agreement between Stiletti annotations (see qc html) and ours 

```{r umap_vln_plots_rna, results='asis', fig.dim = c(10,10), echo=FALSE, warning=FALSE}
umap_vln_plots_rna
```

***

##### Dystonia genes

***

```{r cluster_umap_rna, results='asis', fig.dim = c(10,10), echo=FALSE, warning=FALSE}
dystonia_plot_rna
```

***

#### Refs

***

+ Striatal genes (see WD 2024-03-25 and 2024-04-15 for details):

  + [Anderson et al (2023)](10.1038/s41598-023-36255-5)
  + [Konopka 2023](https://doi.org/10.1038/s41598-023-36255-5)
  + [Lozovaya 2023](https://www.nature.com/articles/s42003-023-05068-7#:~:text=Introduction,activation%20of%20nicotinic%20receptors1.)
  + [Assous and Tepper 2019](https://doi.org/10.1111%2Fejn.13881)
  + [Morgenstern 2022](https://doi.org/10.1126/sciadv.abh4315)
  + [Anderson et al. 2020](https://www.cell.com/cell-reports/fulltext/S2211-1247(20)30191-1?_returnURL=https%3A%2F%2Flinkinghub.elsevier.com%2Fretrieve%2Fpii%2FS2211124720301911%3Fshowall%3Dtrue)
  + [Saunders et al 2018](https://www.cell.com/cell/fulltext/S0092-8674(18)30955-3?_returnURL=https%3A%2F%2Flinkinghub.elsevier.com%2Fretrieve%2Fpii%2FS0092867418309553%3Fshowall%3Dtrue)
  + [Schaaf 2014](https://doi.org/10.1038/gim.2014.9)
  
+ Cer genes (see WD 2024-04-17 for details): 

  + [Yang et al 2024](https://www.nature.com/articles/s41421-024-00656-1?fromPaywallRec=false)
  + [Sepp et al 2023](https://www.nature.com/articles/s41586-023-06884-x?fromPaywallRec=false)
  + [Zhong et al (2023)](https://doi.org/10.1038/s41467-023-43568-6)
  + [Kozareva et al 2021](https://www.nature.com/articles/s41586-021-03220-z)
  + [Aldinger et al 2021](https://www.nature.com/articles/s41593-021-00872-y?fromPaywallRec=false)
  + [Buffo and Rossi 2013](https://www.sciencedirect.com/science/article/pii/S0301008213000701?via%3Dihub)
  

***